CODE CHECK

### 2019-12-06 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/

>>>>

- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
